Positive Correlation Between Racialization, Gendering and Police Strip Searches in the Toronto Municipal, 2020-2021

### 2024-01-26 outputs/paper/paper.qmd
fine-tune writing and finalize paper

Specifically, the column 'Strip Search' signifies whether an arrest involves strip searching. As for the 'Items Found' column, either a `1` or a `0` will appear in a data cell if the 'Strip Search' value of an event is a `1`. This is because the items found within a strip search is only available when a police arrest does involve strip searching.

>>>>

Specifically, the column "Strip Search" signifies whether an arrest involves strip searching. As for the "Items Found" column, either a `1` or a `0` will appear in a data cell if the "Strip Search" value of an event is a `1`. This is because the items found within a strip search is only available when a police arrest does involve strip searching.
